### 2018-05-07 acknowledge.tex
Wrote Thanks

Acknowledgments forthcoming. There are far too many people to thank...

>>>>

The ultimate success of the work presented in this thesis would not have been possible without the continued time and support of numerous individuals I've encounters throughout my life and career.

First, I would like to thank my thesis advisor Edo Berger. It has been a pleasure to work with him during the past five years on such an exciting and novel project. Without his initial push into this field I never would have started this work. I've always appreciated Edo's ability to strike a balance between letting me work on my own and pushing me beyond my limits when the project demanded it. I know his guidance has helped me be not just a better scientist but a better collaborator and member of the community.

Of course, my success in graduate school would not have been possible without the strong foundation I developed in undergraduate. During my time at University of Maryland - College Park, I was fortunate enough to work with Chris Reynolds for four years. His support and knowledge were crucial in my early development as a researcher. I am also thankful to Cole Miller for always providing guidance and forcing me to think about things in new ways.

The Astronomy Department at Harvard has been a phenomenal place to work and there are numerous members of the faculty and staff that I would like to thank. First, I am grateful for the support I've gotten from my committee members: Josh E. Grindlay (Chair), Daniel J. Eisenstein, and Brian D. Metzger (External). I am always appreciative of their advice and feedback. I want to thank other members of the faculty for providing valueable support. Lastly, the department would not be able to run without the tireless efforts of the administrative staff including Lisa Catella, Peg Herlihy, and Robb Scholten.

I am also thankful to the amazing research colleagues and collaborations I have developed during my time in graduate school. First, I am fortunate enough to be involved in a great research group here at Harvard -- The Berger Cosmic Transients Lab. The combined knowledge and talent of everyone involved, both past and present, has been essential in my development as a well-rounded scientist.

I have also been fortunate enough to build collaborations outside of my immediate group at Harvard. First, I would like to thank Brian Metzger, for helping me develop the ``theorist" side of my brain and being an all around fantastic collaborator. I am also thankful to James Guillochon, Dan Holz, Dan Kasen, and Daniel Scolnic for the many many hours they've invested in the development of my work. Looking back over the past five years, I am truly humbled by the amazing people I've been fortunate enough to work with.

To my friends and loved ones, both near and far, who provided much needed outlets from research.

Lastly, to my family, who always enoucouraged me to pursue my interests, no matter what. While this freedom in life ultimately resulted in a circuitous path to this point, I wouldn't be who I am otherwise.
